---
output:
  word_document: default
  pdf_document: default
  html_document: default
---

#1(4.3)  The effect of four chemical agents on the strength of a particular type of cloth.

```{r}
setwd('C:/Users/Dasha/Desktop/6357_Linear Models and Design of Experiments_Wang/HW_6357/HW4')
data = read.delim('CH04PR03.txt')
data$Chemist = as.factor(data$Chemist)
data$Bolt = as.factor(data$Bolt)
fit = lm(Strength ~ Chemist + Bolt, data = data)
anova_res = aov(fit)
summary(anova_res)
plot(anova_res)
```
#2(4.10) Shape factor was determined for several different nozzle designs at six levels of jet efﬂux velocity
#a)
```{r}
data = read.delim('CH04PR10.txt')
data$Jet.Velocity = as.factor(data$Jet.Velocity)
data$Nozzle.Design = as.factor(data$Nozzle.Design)
fit = lm(Shape ~ Nozzle.Design + Jet.Velocity, data = data)
anova_res = aov(fit)
summary(anova_res)
```
#Scatter plot Nozzles vs SHape
```{r}
plot(as.numeric(data$Nozzle.Design), data$Shape)
```

#b)Analyze the residuals from this experiment
```{r}
plot(anova_res)
plot(as.numeric(data$Nozzle.Design),fit$residuals)
```
#c)Excluding Velocity from the the model, since velocity -  variable of secondary interest (nuisance parameter). 
```{r}
anova_res = aov(Shape ~ Nozzle.Design, data = data)
summary(anova_res)
plot(anova_res)
plot(as.numeric(data$Nozzle.Design),fit$residuals)
```


#d) Tukey and Bonferonni tests for nozzle designs with respect to shape factor

```{r}
TukeyHSD(aov(lm(Shape ~ Nozzle.Design, data = data)))
plot(TukeyHSD(aov(lm(Shape ~ Nozzle.Design, data = data))))
```

```{r}
pairwise.t.test(data$Shape, data$Nozzle.Design, p.adj = "bonferroni")
```

```{r}
mu = c() 
for (i in 1:5){   
  a = 6*i-5 
  b = 6*i   
  mu[i] = mean(data[a:b,3]) 
  } 
t.val = seq(1,5,0.1) 
dt.val = dt(t.val,30-5) 
plot(mu, ylim = c(0,1))
plot(t.val, dt.val, type='l', ylim = c(0,1)) 
```

#3(4.11)  Different algorithms for estimating software development costs. Six algorithms were applied to several different software development projects and the percent error in estimating the development cost was observed.
#a)
```{r}
data = read.delim('CH04PR11.txt')
data$Project = as.factor(data$Project)
data$Algorithm = as.factor(data$Algorith)
fit = lm(Cost.Error ~ Algorithm + Project, data = data)
anova_res <- aov(fit)
summary(anova_res)
```
#b)Residuals plots
```{r}
plot(anova_res)
plot(as.numeric(data$Algorithm),fit$residuals)
```
#c)
```{r}
plot(as.numeric(data$Algorithm), data$Cost.Error)
summary(fit)
model.tables(anova_res,"means")
```

#4 Coding practice
#1)The ﬁrst level of each variable as the reference level (by default, R use the first level as reference)
```{r}
data = read.table('HW4_tirebrand.txt', header = TRUE)
data$Road = as.factor(data$Road)
data$Brand = as.factor(data$Brand)
fit1 = lm(Treat ~ Road*Brand, data = data)
anova(fit1)
summary(fit1)
model.matrix(fit1)

```

#2) The second level of each variable as the reference level 
```{r}
data$Road <- relevel(data$Road, ref = "Concrete")
data$Brand <- relevel(data$Brand, ref = "Y")
fit2 = lm(Treat ~ Road*Brand, data = data)
anova(fit2)
summary(fit2)
model.matrix(fit2)
```

#3) The last level of each variable as the reference level 
```{r}
data$Road <- relevel(data$Road, ref = "Gravel")
data$Brand <- relevel(data$Brand, ref = "Z")
fit3 = lm(Treat ~ Road*Brand, data = data)
anova(fit3)
summary(fit3)
model.matrix(fit3)
```
#4) The centralization side condition, eﬀect estimate and the conﬁdence interval band
```{r}
data = read.table('HW4_tirebrand.txt', header = TRUE)
data$Road = as.factor(data$Road)
data$Brand = as.factor(data$Brand)
model.matrix(~ Road+Brand, data = data, contrasts.arg = list(Road = "contr.sum", Brand = "contr.sum"))
```
#5) Analyse the data and show the eﬀects of factors in plots of pairs
#There is an interaction effect among the road type and tire brand.
Reference level: Road(Asphalt) and Brand(X)
```{r}
pairs(Treat ~ Road*Brand, data = data)
```
Reference level: Road(Concrete) and Brand(Y)
```{r}
data$Road <- relevel(data$Road, ref = "Concrete")
data$Brand <- relevel(data$Brand, ref = "Y")
pairs(Treat ~ Road*Brand, data = data)
```
Reference level: Road(Gravel) and Brand(Z)
```{r}
data$Road <- relevel(data$Road, ref = "Gravel")
data$Brand <- relevel(data$Brand, ref = "Z")
pairs(Treat ~ Road*Brand, data = data)
```

#Since the lines in the plots are not parallel to each other, the interaction between selected factors does exist and should be taken into consider.
```{r}
interaction.plot(data$Road, data$Brand, data$Treat)
```
```{r}
interaction.plot(relevel(data$Road, ref = "Concrete"), relevel(data$Brand, ref = "Y"), data$Treat)
```

```{r}
interaction.plot(relevel(data$Road, ref = "Gravel"), relevel(data$Brand, ref = "Z"), data$Treat)
```
